
---
title: "logsAnalysiswithSparkRandSparklyR"
output:
  html_document:
    toc: true
---

##3.1 Log Analysis with SparkR

```{r}
library(SparkR)
library(stringr)
file_location = "/FileStore/tables/NASA_access_log_Jul95.gz"
file_location = "/FileStore/tables/NASA_access_log_Aug95.gz"
# Load the SparkR library


# Initiate a SparkR session
sparkR.session()
sc <- sparkR.session()
sqlContext <- sparkRSQL.init(sc)
df <- read.text(sqlContext,"/FileStore/tables/NASA_access_log_Jul95.gz")

#df=SparkR::select(df, "value")
#head(SparkR::collect(df))
#m=regexp_extract(df$value,'\\\\S+',1)

a=df %>% 
  withColumn('host', regexp_extract(df$value, '^(\\S+)', 1)) %>%
  withColumn('timestamp', regexp_extract(df$value, "((\\S+ -\\d{4}))", 2)) %>%
  withColumn('path', regexp_extract(df$value, '(\\"\\w+\\s+([^\\s]+)\\s+HTTP.*")', 2))  %>%
  withColumn('status', regexp_extract(df$value, '(^.*"\\s+([^\\s]+))', 2)) %>%
  withColumn('content_size', regexp_extract(df$value, '(^.*\\s+(\\d+)$)', 2))
#b=a%>% select(host,timestamp,path,status,content_type)
head(SparkR::collect(a),10)

```

##3.11 Compute count of hosts

```{r}
c <- SparkR::select(a,a$host)
df=SparkR::summarize(SparkR::groupBy(c, a$host), noHosts = count(a$host))
df1 =head(arrange(df,desc(df$noHosts)),10)
head(df1)
```

##3.12 Plot count of hosts

```{r}
library(ggplot2)
p <-ggplot(data=df1, aes(x=host, y=noHosts,fill=host)) +   geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + xlab('Host') + ylab('Count')
p
```

##3.13 Compute count of HTTP requests

```{r}
library(SparkR)
c <- SparkR::select(a,a$path)
df=SparkR::summarize(SparkR::groupBy(c, a$path), numRequest = count(a$path))
df1=head(df)
```

##3.14 Plot count of HTTP Requests

```{r}
library(ggplot2)
p <-ggplot(data=df1, aes(x=path, y=numRequest,fill=path)) +   geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))+ xlab('Path') + ylab('Count')
p
```

##3.15  Compute count of HTTP Response status

```{r}
library(SparkR)
c <- SparkR::select(a,a$status)
df=SparkR::summarize(SparkR::groupBy(c, a$status), numStatus = count(a$status))
df1=head(df)

```

##3.16 Plot count of HTTP Response status

```{r}
library(ggplot2)
p <-ggplot(data=df1, aes(x=status, y=numStatus,fill=status)) +   geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + xlab('Status') + ylab('Count')
p
```

##3.17 Compute count of content size

```{r}
library(SparkR)
c <- SparkR::select(a,a$content_size)
df=SparkR::summarize(SparkR::groupBy(c, a$content_size), numContentSize = count(a$content_size))
df1=head(df)
df1
```

## 3.16 Plot count of content sizes

```{r}
library(ggplot2)
p <-ggplot(data=df1, aes(x=content_size, y=numContentSize,fill=content_size)) +   geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + xlab('Content Size') + ylab('Count')
p

```

##3.21 Log Analysis with SparklyR

```{r}
install.packages("sparklyr")
library(sparklyr)
library(dplyr)
library(stringr)
#sc <- spark_connect(master = "local", version = "2.1.0")
sc <- spark_connect(method = "databricks")
sdf <-spark_read_text(sc, name="df", path = "/FileStore/tables/NASA_access_log*.gz")
sdf
```


```{r}
#install.packages("sparklyr")
library(sparklyr)
library(dplyr)
library(stringr)
#sc <- spark_connect(master = "local", version = "2.1.0")
sc <- spark_connect(method = "databricks")
sdf <-spark_read_text(sc, name="df", path = "/FileStore/tables/NASA_access_log*.gz")
sdf <- sdf %>% mutate(host = regexp_extract(line, '^(\\\\S+)',1)) %>% 
               mutate(timestamp = regexp_extract(line, '((\\\\S+ -\\\\d{4}))',2)) %>%
               mutate(path = regexp_extract(line, '(\\\\"\\\\w+\\\\s+([^\\\\s]+)\\\\s+HTTP.*")',2)) %>%
               mutate(status = regexp_extract(line, '(^.*"\\\\s+([^\\\\s]+))',2)) %>%
               mutate(content_size = regexp_extract(line, '(^.*\\\\s+(\\\\d+)$)',2))

```

##3.22 Compute count of Hosts

```{r}
df <- sdf %>% select(host,timestamp,path,status,content_size)
df1 <- df %>% select(host) %>% group_by(host) %>% summarise(noHosts=n()) %>% arrange(desc(noHosts))
df2 <-head(df1,10)
```

##3.23 Plot count of hosts

```{r}
library(ggplot2)
p <-ggplot(data=df2, aes(x=host, y=noHosts,fill=host)) +   geom_bar(stat="identity")+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) + xlab('Host') + ylab('Count')
p

```

##3.24 Compute count of paths

```{r}
df <- sdf %>% select(host,timestamp,path,status,content_size)
df1 <- df %>% select(path) %>% group_by(path) %>% summarise(noPaths=n()) %>% arrange(desc(noPaths))
df2 <-head(df1,10)
df2
```

##3.25 Plot count of Paths

```{r}
library(ggplot2)
p <-ggplot(data=df2, aes(x=path, y=noPaths,fill=path)) +   geom_bar(stat="identity")+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) + xlab('Path') + ylab('Count')
p
```

##3.26 Compute count of status

```{r}
df <- sdf %>% select(host,timestamp,path,status,content_size)
df1 <- df %>% select(status) %>% group_by(status) %>% summarise(noStatus=n()) %>% arrange(desc(noStatus))
df2 <-head(df1,10)
df2
```

##3.27 Plot count of status

```{r}
library(ggplot2)
p <-ggplot(data=df2, aes(x=status, y=noStatus,fill=status)) +   geom_bar(stat="identity")+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) + xlab('Status') + ylab('Count')
p
```

##3.28 Compute count of content_size

```{r}
df <- sdf %>% select(host,timestamp,path,status,content_size)
df1 <- df %>% select(content_size) %>% group_by(content_size) %>% summarise(noContentSize=n()) %>% arrange(desc(noContentSize))
df2 <-head(df1,10)
df2
```

##3.29 Plot count of content_size

```{r}
library(ggplot2)
p <-ggplot(data=df2, aes(x=content_size, y=noContentSize,fill=content_size)) +   geom_bar(stat="identity")+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) + xlab('Content size') + ylab('Count')
p
```


```{r}

```

